Make any stupid plot you want

### 2021-01-26 draft/sections/math.tex
finished out graphics section

\subsubsection{Data: Sections $\tau$}
\label{sec:data_section}
While the fiber and base space describe the general structure of all data that lives in the fiber bundle, the sections $\tau: K\rightarrow E$ define the datasets that live in the fiber. We generalize Spivak's section as table $\tau$\cite{spivakSIMPLICIALDATABASES} to any sort of structured dataset such that 
\begin{equation}
    \label{eq:section}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']           
        & K \arrow[u, "\tau"', bend right]
    \end{tikzcd}
\end{equation}
such that there is $\pi(\tau(k)) = k$ map back to $K$. There can be many sections $\tau$, and the space of global sections is $\Gamma(E)$. For a trivial fiber bundle
\begin{equation}
    \label{eq:section_return}
    \tau(k) = (k, (g_{F_{0}}(k), \ldots, g_{F_{n}}(k))
\end{equation}
where $g: K \rightarrow F$ is the index function into the fiber. Because we can decompose the bundle and the fiber, we can formulate $\tau$ as 
\begin{align}
\tau = (\tau_0,\ldots, \tau_i, \dots, \tau_n) 
\end{align}
where each section $\tau_i$ is a variable or set of variables.

@@

\subsubsection{Display $D$}
\label{sec:graphic_fiber}
The fiber $D$ is specified in terms of the target display space, for example a 2D screen or 3D printer. In this work, we assume a simple 2D opaque image $D=\mathbb{R}^5$ with a record $d \in D$ of the form
\begin{equation}
    d = (x, y, R, G, B)
\end{equation}
such that a graphic only has 2D position and color. To support overplotting and transparency, the fiber would be $D=R^{7}$ such that $d=(x,y,z, R, G, B, A)$. The location coordinates $x$ and $y$ are defined in terms of the display, while the \textrm{R,G,B} values are filled in via a lookup on $S$.

@@

\subsubsection{Renderable Glyph $\rho$}
\label{sec:graphic_section}
A section $\rho: S \rightarrow H$ is a mapping from a region $s$ on a mathematical encoding of the image to a region $xy$ on the screen that the renderer then maps to visual space as defined in D.

We define a section of the displayed graphic as a region on D defined by the bounding box $b=\left[y_{top}, y_{bottom}, x_{right}, x_{left}\right]$

\paragraph{Example}
For a physical screen display, we can consider a predisplay space that is a trivial fiber bundle $H=\mathbb{R}^{5}\times S$ such that $\rho$ is
\begin{equation}
    \rho(s)  = (D_x(s), D_y(s), D_r(s), D_g(s), D_b(s))
    \label{eq:rho}
\end{equation}

To draw an image, a region, $H$ is inverse mapped into a region $s \in S$ where %%% 
\begin{equation}
s = \rho^{-1}_{\tiny{XY}}(xy)
\end{equation}
such that the rest of the fields in $\mathbb{R}^{7}$ are then integrated over $s$ to yield the remaining fields
%% redefining notation 
\begin{align}
    R_b &= \iint\limits_s D_r(s)ds^{2}\\
    G_b &= \iint\limits_s D_g(s)ds^{2}\\
    B_b &= \iint\limits_s D_b(s)ds^{2}
\end{align}

Here we assume a single opaque 2D image such that the $z$ and $alpha$ fields can be omitted. To support overplotting and transparency, we can consider $D=R^{7}$

\subsubsection{{Example}}
\begin{figure}[H]
    \includegraphics[width=.4\linewidth]{figures/math/render.png}
    \caption{}
    \label{fig:render}
\end{figure}

As illustrated in figure~\ref{fig:render}, words.

>>>>

\subsubsection{Data: Sections $\tau$}
\label{sec:data_section}
While the fiber and base space describe the general structure of all data that lives in the fiber bundle, the sections $\tau: K\rightarrow E$ define the datasets that live in the fiber. We generalize Spivak's section as table $\tau$\cite{spivakSIMPLICIALDATABASES} to any sort of structured dataset such that 
\begin{equation}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi"']              \\
                          & K \arrow[u, "\tau"', bend right]
    \end{tikzcd}
\end{equation}
such that there is $\pi(\tau(k)) = k$ map back to $K$. There can be many sections $\tau$, and the space of global sections is $\Gamma(E)$. For a trivial fiber bundle
\begin{equation}
    \label{eq:section_return}
    \tau(k) = (k, (g_{F_{0}}(k), \ldots, g_{F_{n}}(k))
\end{equation}
where $g: K \rightarrow F$ is the index function into the fiber. Because we can decompose the bundle and the fiber, we can formulate $\tau$ as 
\begin{align}
\tau = (\tau_0,\ldots, \tau_i, \dots, \tau_n) 
\end{align}
where each section $\tau_i$ is a variable or set of variables.

@@

\subsubsection{Display $D$}
\label{sec:graphic_fiber}
The fiber $D$ is specified in terms of the target display space, for example a 2D screen or 3D printer. In this work, we assume a simple 2D opaque image $D=\mathbb{R}^5$ with a record $d \in D$ of the form
\begin{equation}
    d = (x, y, r, g, b)
\end{equation}
such that a graphic only has 2D position and color. To support overplotting and transparency, the fiber would be $D=R^{7}$ such that $d=(x, y, z, r, g, b, a)$. The location coordinates $x$ and $y$ are defined in terms of the display, while the $(r,g,b)$ values are filled in via a lookup on $S$.

@@

\subsubsection{Renderable Glyph $\rho$}
\label{sec:graphic_section}

A section $\rho: S\rightarrow H$ defines a piece of the graphical representation of the data. The physical display coordinates in $D$ are not equivalent to the mathematical coordinates in $S$ such that many points $s \in S$ might map to a single $d\in D$ and many $d$ might go into a visible section of a displayed graphic. Therefore, we define the bounding box $b=\left[y_{top}, y_{bottom}, x_{right}, x_{left}\right]$ in the display space $D$ that is a piece of the rendered graphic.

We inverse map this bounding box $S_b =\rho^{-1}(b)$ into a region $S_b \subset S$  
\begin{align}
    R_b &= \iint\limits_{S_b} \rho_r(s)ds^{2}\\
    G_b &= \iint\limits_{S_b} \rho_g(s)ds^{2}\\
    B_b &= \iint\limits_{S_b} \rho_b(s)ds^{2}
\end{align}
to then compute the remaining $(R, G, B)$ components of the bounded display region $D_b$.

\begin{figure}
    \includegraphics[width=\textwidth]{figures/math/graphic_render.png}
    \caption{To render a graphic, a region $b$ is selected in the display space. This region is in coordinates $D$ so the inverse mapping $\rho^{-1}(b)$ maps to an equivalent region $S_b \subset S$. We then take the sections $\rho(S_b)$ which are the collection of records $d$ that combine together to make the piece of the graphic in $b$.}
    \label{fig:graphic_rho_lookup}
\end{figure}
As shown in figure~\ref{fig:graphic_rho_lookup}, the output space queries into the graphic bundle to render the image. We select a region $b$ in the output space, inverse map the region into $S_b \subset S$, then take the section $\rho$ over the region $S_b$ which yields a set of corresponding records $d$. These records specify the $(r, g, b)$ values corresponding to the coordinates in $b$. These records are then combined to render the piece of the graphic in $b$.
